---
output: 
  html_document:
    toc: TRUE
    toc_depth: 2
      
params:
  name: "candidate name"
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
```


```{r}
#filter responses to only include responses for 1 candidate
responses_mayor <- subset(responses_mayor, name == name)
```

# Responses from `r responses_mayor$name`

## How candidates move around the city

### `r questions$q_text[3]`
`r responses_mayor$last_bus`

### `r questions$q_text[4]`
`r responses_mayor$last_bike`

### `r questions$q_text[5]`
`r responses_mayor$get_around`

## Madison Bikes questions

### `r questions$q_text[which(questions$q_label == "MB_network")]`
`r responses_mayor$MB_network`

### `r questions$q_text[which(questions$q_label == "MB_climate")]`
`r responses_mayor$MB_climate`

### `r questions$q_text[which(questions$q_label == "MB_policies")]`
`r responses_mayor$MB_policies`

## Madison is for People questions

### `r questions$q_text[which(questions$q_label == "MIFP_preservation")]`
`r responses_mayor$MIFP_preservation`

### `r questions$q_text[which(questions$q_label == "MIFP_affordability")]`
`r responses_mayor$MIFP_affordability`

### `r questions$q_text[which(questions$q_label == "MIFP_zoning")]`
`r responses_mayor$MIFP_zoning`

## Madison Area Bus Advocates questions

### `r questions$q_text[which(questions$q_label == "MABA_vision")]`
`r responses_mayor$MABA_vision`

### `r questions$q_text[which(questions$q_label == "MABA_funding")]`
`r responses_mayor$MABA_funding`

### `r questions$q_text[which(questions$q_label == "MABA_accessibility")]`
`r responses_mayor$MABA_accessibility`





```{r}
params$title
```






